R for Clinical Study Reports and Submission

### 2021-11-19 index.Rmd
automate rtf to pdf conversion

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "#>", echo = TRUE, message = FALSE)
options(dplyr.summarise.inform = FALSE)
file.copy("static/CNAME", "_book", overwrite = TRUE)
fs::dir_copy("slides/", "_book/slides", overwrite = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "#>", echo = TRUE, message = FALSE)
options(dplyr.summarise.inform = FALSE)
```

@@

```{r, include=FALSE}
source("common.R")
```
